---
categories:  
- ""    #the front matter should be like the one found in, e.g., blog2.md. It cannot be like the normal Rmd we used
- ""
date: "2021-09-30"
description: German election polls over time  # the title that will show up once someone gets to this page
draft: false
image:  # save picture in \static\img\blogs. Acceptable formats= jpg, jpeg, or png . Your iPhone pics wont work

keywords: ""
slug: german_polls # slug is the shorthand URL address... no spaces plz
title: The German election polls
---
  



```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=8, 
  fig.height=8,
  fig.align = "center"
)
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest) # to scrape wikipedia page
library(kableExtra)
```





```{r, scrape_wikipedia_polling_data, warnings= FALSE, message=FALSE}
url <- "https://en.wikipedia.org/wiki/Opinion_polling_for_the_2021_German_federal_election"

# similar graphs and analyses can be found at 
# https://www.theguardian.com/world/2021/jun/21/german-election-poll-tracker-who-will-be-the-next-chancellor
# https://www.economist.com/graphic-detail/who-will-succeed-angela-merkel


# get tables that exist on wikipedia page 
tables <- url %>% 
  read_html() %>% 
  html_nodes(css="table")


# parse HTML tables into a dataframe called polls 
# Use purr::map() to create a list of all tables in URL
polls <- map(tables, . %>% 
             html_table(fill=TRUE)%>% 
             janitor::clean_names())


# list of opinion polls
german_election_polls <- polls[[1]] %>% # the first table on the page contains the list of all opinions polls
  slice(2:(n()-1)) %>%  # drop the first row, as it contains again the variable names and last row that contains 2017 results
  mutate(
         # polls are shown to run from-to, e.g. 9-13 Aug 2021. We keep the last date, 13 Aug here, as the poll date
         # and we extract it by picking the last 11 characters from that field
         end_date = str_sub(fieldwork_date, -11),
         
         # end_date is still a string, so we convert it into a date object using lubridate::dmy()
         end_date = dmy(end_date),
         
         # we also get the month and week number from the date, if we want to do analysis by month- week, etc.
         month = month(end_date),
         week = isoweek(end_date)
         )

german_election_polls0<-german_election_polls
german_election_polls<- german_election_polls %>% 
  arrange(end_date) %>% 
  group_by(end_date) %>% 
  summarise(CDU_m=mean(union),spd_m=mean(spd),afd_m=mean(af_d),fdp_m=mean(fdp),linke_m=mean(linke),grune_m=mean(grune))
  

election_rolling_mean <- german_election_polls %>%   # this is a new object
  mutate( 
    #calculate 3-day rolling average
    CDU=zoo::rollmean(CDU_m, k=14, fill = NA),
    afd=zoo::rollmean(afd_m, k=14, fill = NA),
    spd = zoo::rollmean(spd_m, k=14, fill = NA),
    fdp = zoo::rollmean(fdp_m, k=14, fill = NA),
    linke= zoo::rollmean(linke_m, k=14, fill = NA),
    grune = zoo::rollmean(grune_m, k=14, fill = NA)
    ) 

election_rolling_mean<-na.omit(election_rolling_mean)
election_rolling<-data.frame(x=unlist(election_rolling_mean[,8:13]))
election_rolling[,2]<-rep(c("CDU","afd","spd","fdp","linke","grune"),each=nrow(election_rolling_mean))
election_rolling[,3]<-rep(election_rolling_mean$end_date,6)
names(election_rolling)[2]<-"Parties"

p<-data.frame(x=unlist(german_election_polls0[,5:10]))
p[,2]<-rep(c("CDU","spd","afd","fdp","linke","grune"),each=nrow(german_election_polls0))
p[,3]<-rep(c(german_election_polls0$end_date),6)


ggplot() +
  geom_line(data=election_rolling, aes(x=V3,y=x,colour=Parties)) +
  ylim(0, 50)+
  geom_point(data=p,aes(y=x,x=V3,colour=V2),alpha=0.5,size=1)+
  scale_x_date(date_labels = "%d/%b/%Y")+
  theme_bw()+
    theme(legend.position = "none")+
    labs(
    title = "German Election Poll vs. Time",
    x = "date",
    y = "14-day rolling average %",
    )+
  theme(plot.title = element_text(size=18),plot.subtitle = element_text(size=16),axis.title.x =element_text(size = 14),axis.title.y = element_text(size = 14))+
  scale_color_manual(values = c("blue","black" , "yellow","green","purple","red"))+
  theme(legend.position="right")+
    NULL
```


## Opinion

Here you can see the development of the German election polls over time as well as a 14-day rolling average. Some interesting shifts in the support for the CDU can be observed. Armin Laschet, frontrunner of the CDU, was made responsible for this, as he could not convince voters in public discussions. Most of the prior CDU voters shifted to SPD and their frontrunner Olaf Scholz.





